### 2018-09-04 sections/signal_background_modeling.tex
trigger-matching, fake estimate for tautau

This background is estimated directly from data by defining control regions (CR) enriched in fake $\tauhad$ candidates via loosened $\tauhad$ requirements. These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}. The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\tauhad$ candidate 
in the $\lephad$ ($\hadhad$) channel is required to be of loose-not-medium quality, and the requirement on its charge is removed.

>>>>

This background is estimated directly from data by defining control regions (CR) enriched in fake $\tauhad$ candidates via loosened $\tauhad$ requirements or flipped charge. These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}. The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\tauhad$ candidate 
in the $\lephad$ ($\hadhad$) channel is required to fail the medium tau identification but pass the loose one, or the two tau candidates have the same charge.
